---
title: "2021-10-31-ST558-Project2-Blog"
author: "Ilana Feldman"
date: "10/31/2021"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r eval = FALSE, echo = FALSE}
rmarkdown::render("./_Rmd/2021-10-31-ST558-Project2-Blog.Rmd",
                  output_format = "github_document",
                  output_dir = "./_posts/",
                  output_options = list(html_preview = FALSE)
)
```

# Project 2 Report

The first project was extremely distressing for me to work on even though the final product ended up adhering to all of the important requirements, and I wasn't looking forward to working on another one, even if it was with another person. As a result, the hardest part was actually getting started on the meat of the project. As the first group member, I created the project repo page and shared it with my partner, but I found the remaining instructions very confusing from the outset, and by the time I buckled down to start working on it, I was immediately overwhelmed and disoriented by the work my project partner had already done into setting everything up. There are a few loose ends of our project that didn't get resolved in a satisfactory way, and I feel like, if I had really gotten involved in the setup process more, I could have helped diagnose and fix the problems before the deadline.

The resulting dynamic of the project was, in the end, me tip-toeing around the excellent work my partner did and adding my parts, as well as keeping communications open to make sure I was on the same page. While I do feel like I was able to do my fair share of work in the end, the slow start and initial disorientation made the experience a lot more unpleasant than it should have been, especially since my partner was friendly, capable, and responsive. I think the clear takeaway here is that it's very important to be involved in the setup when a project has this short of a timeline.

The link to the project output page can be found [here](https://ilanafeldman.github.io/ST558-Project-2/) and the link to the project repo page can be found [here](https://github.com/IlanaFeldman/ST558-Project-2).